Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Modify 'sensor' to 'streaming data sources'

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.

@@

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream. They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their sensors.

\subsubsection{Consumer}
Consumers aspire to obtain IoT data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the IoT data from data providers. They search products on the marketplace and pay for subscription fee. While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically. The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains sensing data.

@@

To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}). Each product has a Product Contract to record the trading process.

@@

The whole trading process is shown in Figure \ref{fig:trading_product}. Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.

@@

Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

>>>>

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade in streaming data subscription.

@@

\subsubsection{Data Provider}
Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream. They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the streaming data from data providers. They search products on the marketplace and pay for subscription fee. While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically. The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains streaming data.

@@

To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}). Each product has a Product Contract to record the trading process.

@@

The whole trading process is shown in Figure \ref{fig:trading_product}. Once a consumer who want to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.

@@

Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted data is uploaded to the MAM channel, and consumers can download and decrypt it with the session key.

\subsection{Refunding}
It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:
